---
title: "Alaphabet Time Series Analysis"
author: "Daniel Byrne"
date: "10/29/2019"
output:
  word_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tswge)
library(tseries)

library(orcutt)

# Get quantmod
if (!require("quantmod")) {
    install.packages("quantmod")
    library(quantmod)
}

start <- as.Date("2016-01-01")
end <- as.Date("2019-10-01")

getSymbols("GOOGL", src = "yahoo", from = start, to = end)
```


## Google Closing Stock Price

Wandering in the time series realization and slowly damping ACF indicate the presence of at least one unit root.

```{r}
googl = GOOGL$GOOGL.Close 
plotts.sample.wge(googl)
```

Overfitting indicates the possible presence of at least one unit root.
```{r}
best = est.ar.wge(googl,p=8,type="burg")
```

Dickey Fuller also indicates the presence of a unit root.
```{r}
adf.test(googl)
```

## ARIMA

```{r}
xd1 = artrans.wge(googl,phi.tr = 1)
```

```{r}
aic5.wge(xd1)
amodel = est.arma.wge(xd1,p=2,q=2)

#final model
amodel$phi
amodel$theta
amodel$avar
d=1
```

- phi = `r amodel$phi`
- theta = `r amodel$theta`
- avar = `r amodel$avar`
- d = 1

## Seasonal

Stock data is potentially seasonal, so I attempt to difference a quarterly trend

```{r}
xs4 = artrans.wge(googl,phi.tr = c(0,0,0,1),plottr = TRUE)
aic5.wge(xs4)
u = mean(googl)
u

smodel = est.arma.wge(xs4,p=4,q=1)
```

- phi = `r smodel$phi`
- theta = `r smodel$theta`
- avar = `r smodel$avar`
- d = 1

## Sig-Plus Noise

### lm 

```{r}
z <- fortify.zoo(googl, name = "Date")
x <- z$GOOGL.Close
t = seq(1,length(x),1)
df = data.frame(x = x, t= t)
fit = lm(x~t, data = df)
summary(fit)
```

### Chochrane-Orcutt 

```{r}

cfit = cochrane.orcutt(fit)
summary(cfit)
```


## Apple Stock

```{r}
getSymbols("AAPL", src = "yahoo", from = start, to = end)
aapl = AAPL$AAPL.Close
plotts.sample.wge(aapl)
ad1 = artrans.wge(aapl,phi.tr = 1)
aic5.wge(ad1)
```

Final model is simply the variance of the signal data



