---
title: "Unit5"
author: "Daniel Byrne"
date: "9/24/2019"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tswge)
library(mosaic)
# Read in the data
Walmart = read.csv('Walmart.csv',header = TRUE)
swadelay = read.csv('swadelay.csv',header=TRUE)

# Load the Data
Stor8Item1 = Walmart %>% filter(item == 1 & store == 8)#Look at and Visualize the data
```



Slide 1: Use Aic5 to assess the use of ARMA models in the Walmart data.

```{r}
aic5.wge(Stor8Item1$sales,p=10:15, q=0:5)
```

Slide 2: Find p1 for the following model by hand.  Xt = at–.8at-1 + .5at–2.
```{r}
theta1 = .5
theta2 = -.5
p1 = (-theta1 + theta1*theta2)/(1 + theta1^2 + theta2^2)

#p1
ans = -theta1/(1+theta1^2)
ans
```

Slide 3: Represent the model as a GLP.

`Xt = at–.8at-1 + .5at–2`


Slide 4: Generate a realizations from an ARMA model.  \You pick p and q.  Include the ACF and spectral density. 
```{r}
gen.arma.wge(n=100, phi=c(1.6,-.9), theta=.8, vara=1, plot=TRUE)
```

Slide 5: Use AIC 5 to identify the top five quality models with respect to AIC for the cancelled flight data from the SWADelay.csv data set (column: arr_cancelled). Comment on which are AR, MA, and ARMA.

- row 1 AR Model
- row 2 MA Model
- row 3 AR Model
- row 4 ARMA Model
- row 5 MA Model

```{r}
aic5.wge(swadelay$arr_cancelled)
```
