---
title: "Unit 13 In Class Assignment"
author: "Daniel Byrne"
date: "11/19/2019"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tswge)
library(nnfor)
ss = read.csv("Unit 13/Melanoma_Sunspot.csv")
pol = read.csv("Unit 13/LA_Cmort_Study.csv")

swa = read.csv("swadelay.csv")
swa = read.csv("Unit 13/swadelay.csv")


## RNN Analysis of Sunspot Data

Predicting Melonoma using Sunspot and previous Melonoma data.
```{r}
sstrain = ts(ss$Melanoma[1:29],start= c(1936,1),frequency = 1)
sstest =  ts(ss$Melanoma[30:37],start= c(1965,1),frequency = 1)

set.seed(2)

melonomatrain = data.frame(ts(ss$Sunspot,start= c(1936,1),frequency = 1))
fit.mlp = mlp(sstrain, hd.auto.type = "elm", xreg = melonomatrain)
fit.mlp
plot(fit.mlp)
fore.mlp = forecast(fit.mlp, h = 8,xreg = melonomatrain)
plot(fore.mlp, main="Melonoma Forecasts using Sunspot Yearly Data")
ASE = mean((sstest - fore.mlp$mean)^2)
ASE
```

## RNN Analysis of Pollution Data to Predict Mortality

```{r}
train = ts(pol$cmort[1:498],start=1,frequency = 1)
test =  ts(pol$cmort[499:508],start=499,frequency = 1)

set.seed(2)

regs = data.frame(temp=ts(pol$temp,frequency = 1),part =ts(pol$part,frequency = 1))
fit.mlp = mlp(train, hd.auto.type = "elm", xreg = regs)
fit.mlp
plot(fit.mlp)
fore.mlp = forecast(fit.mlp, h = 10,xreg = regs)
plot(fore.mlp)
ASE = mean((test - fore.mlp$mean)^2)
ASE
```

### Google Stock Price Predictions using RNN

```{r}
# Get quantmod
if (!require("quantmod")) {
    install.packages("quantmod")
    library(quantmod)
}

start <- as.Date("2016-01-01")
end <- as.Date("2019-10-01")

getSymbols("GOOGL", src = "yahoo", from = start, to = end)
```

```{r}
googl = GOOGL$GOOGL.Close
z <- fortify.zoo(GOOGL, name = "Date")
train = ts(z$GOOGL.Close[1:(nrow(z)-10)],start=1,frequency = 1)
test = ts(z$GOOGL.Close[(nrow(z)-10):nrow(z)],start=(nrow(z)-10),frequency = 1)

regs = data.frame(volume = ts(z$GOOGL.Volume, frequency = 1),high = ts(z$GOOGL.High,frequency = 1),low = ts(z$GOOGL.Low,frequency = 1))

set.seed(2)
fit.mlp = mlp(train, hd.auto.type = "elm",xreg=regs)
fit.mlp

plot(fit.mlp)

fore.mlp = forecast(fit.mlp, h = 10,xreg=regs)
plot(fore.mlp)
ASE = mean((test - fore.mlp$mean)^2)
ASE
```

## Key Takeaways
```{r}
sstrain = ts(ss[1:29,],start= c(1936,1),frequency = 1)
sstraintest =  ts(ss[30:37,],start= c(1965,1),frequency = 1)
set.seed(2)
fit.mlp = mlp(sstrain,reps = 50,comb = "mean", hd.auto.type = "elm")
fit.mlp
plot(fit.mlp)
fore.mlp = forecast(fit.mlp, h = 36)
plot(fore.mlp)
ASE = mean((SWATest - fore.mlp$mean)^2)
ASE



