---
title: "Time Series Notes"
author: "Daniel Byrne"
date: "10/12/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tswge)
library(mosaic)
if(!exists("foo", mode="function")) source("utilities.r")
```


## Generate Signails

```{r}

# generate a signal with signal plus noise
# coef = coefficients to cosine function
# freq =  (cos argument (not including 2pi))
# psi = phase offset
s=gen.sigplusnoise.wge(100,coef=c(3,1.5),freq = c(.05,.35), psi = c(0,2),vara = 3, plot = FALSE)
plotts.sample.wge(s)
```
## Basic Calculations

## Calculate gamma
```{r}
d = c(1,2,3,4,5,6)
g1 = ts.gamma(d,1)
g1
```

## Calculate gamma0
```{r}
d = c(1,2,3,4,5,6)
rho1 = ts.rho(d,1)
rho1
```

## Frequency Domain
Consider sin(Bt + C)

- Period = 2pi/B
- Frequency = B/2pi

Example : sin(2pi(.17)t)

- Period = 2pi/(2pi*.17) = 1/.17 
- Frequency = 2pi*.17/2pi = .17


### Signal is sum of other signals
```{r}
t = seq(1,100,length = 100)
y1 = sin(2*pi*.025*t)
y2 = sin(2*pi*.1*t+1)
y3 = sin(2*pi*.15*t+2.5)
ysum = y1+y2+y3
plotts.sample.wge(ysum, trunc = 70)
```

```{r}
data(patemp)
parzen.wge(patemp)
```
### Plot Parzen Window

```{r}
data(fig1.21a)
#  trunc = m, ideal is 2*sqrt(n)
# dbcalc - lol 10 base 10 if TRUE
parzen.wge(fig1.21a, dbcalc = TRUE, trunc = 31)
```



### filtering

Generate the realization given by the following code using tswge (Practice by typing it in!):

Use the following code to filter the data generated above: 

ma = filter(Realization,rep(1,5))/5
```{r}
s = gen.sigplusnoise.wge(200,coef = c(5,0),freq = c(.1,0), vara = 10, sn = 1)
ma = filter(s,rep(1,5))/5
plot(ma)
```



