---
title: "Unit 8 FLS"
author: "Daniel Byrne"
date: "10/22/2019"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE, echo=TRUE}
knitr::opts_chunk$set(echo = TRUE)
library(tswge)
tgp = read.csv("texasgasprice.csv")


```

## Texas Gas Price

```{r}
plotts.sample.wge(tgp$Price)
```

## Fitting an AR(2) to the data using MLE
```{r}
mle = est.arma.wge(tgp$Price,p=2,q=0)
```
## Fitting an AR(2) to the data using Burg

```{r}
burg = est.ar.wge(tgp$Price,p=2,type="burg")
```

## Forecasting using the MLE model

```{r}
mlef = fore.aruma.wge(tgp$Price, phi = mle$phi,  n.ahead = 24,  lastn = T, limits = T, plot = T)
```

## Forecasting using the Burg Model

```{r}
burgf = fore.aruma.wge(tgp$Price, phi = burg$phi,  n.ahead = 24,  lastn = T, limits = T, plot = T)
```

## Calculating ASE for MLE


```{r}
ase = function(f,s) {
  l = length(f) - 1
  ls = length(s)
  ase = mean((f - s[(ls - l):ls])^2)
  return (ase)
}

ase(mlef$f,tgp$Price)
```

## Calculating ASE for Burg

```{r}
ase(burgf$f,tgp$Price)
```

Neither forecast seemed particulally accurate.  I wouldn't choose either model.


## Key Takeaways

How does the AIC model estimation technique work?  It might be nice to go through that math.
